Test functions on Alabama data

### 2016-09-28 Code/Test life expectancy fxs on Alabama.Rmd
more changes to the alabama example

cod.tab.alabama.male.1969$prop1 <- second.strata.cod$cod_prop_death5
cod.tab.alabama.male.1969 <- cod.tab.alabama.male.1969 %>% arrange(COD2, Age2)

ggplot(cod.tab.alabama.male.1969, aes(x=COD2, y=prop1)) + 
  geom_point(aes(col="White")) + geom_point(aes(y=prop2, col="Black")) +
  scale_y_continuous(name = "Proportion dying from specified cause") +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
life.table.whites <- data.frame(life.table(data = first.strata, age.groups = "Age2", num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

life.table.blacks <- data.frame(life.table(data = second.strata, age.groups = "Age2", num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

ggplot(life.table.blacks, aes(x = Age3, y = q_x, col = "q_x: Probability")) + geom_point() + geom_point(aes(y = R_x, col="R_x: Mortality rate")) + scale_y_continuous(name = "Value") + scale_x_continuous(name = "Age") + ggtitle("Examining the relationship between the probability of dying and the mortality rate")

alabama_age_decomp <- le_age_decomp(life.table.blacks, life.table.whites, "Age2")
alabama_age_decomp

>>>>

cod.tab.alabama.male.1969$prop1 <- second.strata.cod$cod_prop_death5
cod.tab.alabama.male.1969 <- cod.tab.alabama.male.1969 %>% arrange(COD2, Age2)
```

```{r exploratory graphs}
ggplot(cod.tab.alabama.male.1969, aes(x=COD2, y=prop1)) + 
  geom_point(aes(col="White")) + geom_point(aes(y=prop2, col="Black")) +
  scale_y_continuous(name = "Proportion dying from specified cause") +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(life.table.blacks, aes(x = Age3, y = q_x, col = "q_x: Probability")) + geom_point() + geom_point(aes(y = R_x, col="R_x: Mortality rate")) + scale_y_continuous(name = "Value") + scale_x_continuous(name = "Age") + ggtitle("Examining the relationship between the probability of dying and the mortality rate")
```

```{r}
life.table.whites <- data.frame(life.table(data = first.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

life.table.blacks <- data.frame(life.table(data = second.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

alabama_age_decomp <- le_age_decomp(life.table1 = life.table.blacks, name.lt1 = "Blacks", 
                                    life.table2 = life.table.whites, name.lt2 = "Whites", age.groups = "Age3")
alabama_age_decomp
